%; /usr/bin/env mkdir -p .build && xelatex -output-directory=.build -halt-on-error $0 && cp .build/*.pdf ./; exit

% Add 'print' as an option in the square bracket to remove colors from this template for printing
\documentclass[]{friggeri-cv}
\begin{document}

\header{Lin}{Chen}{}

% ----------------------------------------------------------------------------------------
% SIDEBAR SECTION
% ----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
  \section{Contacts}
  +1 (650) 307-5688
  \href{mailto:clphoenix37+cv@gmail.com}{clphoenix37@gmail.com}
  \href{https://clphoenix.wordpress.com/}{clphoenix.wordpress.com}
\end{aside}

% ----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
% ----------------------------------------------------------------------------------------

\section{Experience}

Worked in the Department of Volunteer in university:
\begin{enumerate}
\item Files management, hours logging,
\item Taught Chinese \& English in a poor elementary school,
\item Taught math in middle school,
\item Violin performance for a senior center,
\item Charitable sale, Shelter work,
\item International conference, Celebrity Interview.
\end{enumerate}

Dietary Aide in an assisted living facility. Interacted closely with elders (mostly
90+ years old). Learned about customer service. Gained a rare \& dear
perspective of life.

Air Force Reserve. Received military training. Further increased physical and
mental strength.

Planned, coordinated a 3-day-2-night trip for 20+ people in Beijing.

Produced a music video with a 40-person cast. Wrote plot, sourced equipment,
directed the performance, turned the recording into a final DVD. Designed a
poster with PS.

Traveled/stayed extensively in multiple countries, exposed to multiple cultures.

% ----------------------------------------------------------------------------------------
% EDUCATION SECTION
% ----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2012 --- 2014}
  {BA in Applied Mathematics}
  {University of Illinois at Urbana Champaign}
  {}
  % ------------------------------------------------
  \entry{2009 --- 2011}
  {Applied Mathematics}
  {University of Science and Technology Beijing}
  {}
  % ------------------------------------------------
\end{entrylist}

\end{document}
